Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens

### 2014-01-23 limits/ms.tex
Updated figure 3 with AA plots.
Updated text.
Added more plots in fig 3. Added galaxy names to plots.

\newcommand{\mockAA}{{\sc Ssteep-DMshallow}}
\newcommand{\mockAC}{{\sc Ssteep-DMsteep}}
\newcommand{\mockBB}{{\sc Ssteep-DMshallow}}
\newcommand{\mockBC}{{\sc Ssteep-DMsteep}}

@@

\begin{figure*}
  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-a.pdf}\hspace{-2em}
  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-b.pdf}\hspace{-2em}
  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-c.pdf}\\\vspace{-1em}
  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-a.pdf}\hspace{-2em}
  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-b.pdf}\hspace{-2em}
  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-c.pdf}
\caption{
  \hilight{Larger fonts. Do we need both examples?}
Two typical reconstructed lens. Here we present results for a single quad image lensed by the \mockBC{} (upper) and \mockAC{} (lower) mock galaxies.
\textbf{Left:}
The ensemble average arrival time surface, with just the isocontours for the
saddle points drawn. The central diamonds show the reconstructed source
position across the entire ensemble.
\textbf{Middle:}
The surface density. The magenta curve represents the dark matter component,
the yellow curve the stellar component, and the blue curve is the sum of the two.
The black curve comes from the original mass model used to create the lens.
The green vertical lines mark the radial positions of the images. The higher
resolution feature of \Glass\ has been used on the central pixel allowing the
steep profile to be captured.
\textbf{Right:}
The cumulative mass. The error bars on all plots are $1\sigma$, but the grey area shows the full range for DM+Stars (blue).}
\label{reconstruction}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.49\textwidth]{AAferror_profile-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BBferror_profile-1sig.pdf}\\
\includegraphics[width=0.49\textwidth]{ACferror_profile-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BCferror_profile-1sig.pdf}
\caption{\hilight{Add names to plots}. Our main results showing the quality of model recovery \eqnrefp{ferror R} for all our test cases. 
Within
each panel are six groups of results for each of six lens morphologies. Each morphology
considered the presence of time delays (T,t) and a central image (M,m). The black markers are for tests
that did not include the stellar mass as a lower bound constraint, while the red markers
indicate where the stellar mass has been included. Error bars show the $1\sigma$ interval of the model ensemble.}
\label{main results}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.49\textwidth]{AAferror-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BBferror-1sig.pdf}\\
\includegraphics[width=0.49\textwidth]{ACferror-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BCferror-1sig.pdf}
\caption{\hilight{Add names to plots.} Similar to \figref{main results}, we show here the fractional error
for the pixel-wise recovery \eqnrefp{ferror theta} of all models. The colors and labels are the same
as before. Error bars show the $1\sigma$ interval of the model ensemble.}
\label{main results pixel-wise}
\end{figure*}

@@

\begin{figure}[h]
\plottwo{AAExtendedDoubleR1_TmS-shape-hist-11.pdf}{BCZContrastR1R3_TmS-shape-hist-212.pdf}
\caption{ \hilight{Larger labels.} The two plots in the left most column show sample distributions of
  $s=\lambda_1/\lambda_2$, the ratio of the largest to smallest principal axes.
  The upper (poor) plot is from the \mockAA{} galaxy, while the lower (good) plot is
  from the \mockBC{} galaxy. The black vertical lines mark the $2\sigma$
  region and the vertical blue line is the value of $s$ for the corresponding
mock galaxy. }

>>>>

\newcommand{\mockAA}{{\sc star1.0-dmCore}}
\newcommand{\mockAC}{{\sc star1.0-dmCusp}}
\newcommand{\mockBB}{{\sc star1.5-dmCore}}
\newcommand{\mockBC}{{\sc star1.5-dmCusp}}

@@

\begin{figure*}
  \plotthree{BCExtendedDoubleR1_tms-a.pdf} {BCExtendedDoubleR1_tms-b.pdf} {BCExtendedDoubleR1_tms-c.pdf}
  \plotthree{BCExtendedDoubleR1_tmS-a-1.pdf} {BCExtendedDoubleR1_tmS-b-1.pdf} {BCExtendedDoubleR1_tmS-c-1.pdf}
  \plotthree{BCQuadR1a_Tms-a.pdf} {BCQuadR1a_Tms-b.pdf} {BCQuadR1a_Tms-c.pdf}
  \plotthree{AAQuadR1a_Tms-a.pdf} {AAQuadR1a_Tms-b.pdf} {AAQuadR1a_Tms-c.pdf}
\caption{
  \hilight{Larger fonts. Do we need both examples?}
Two typical reconstructed lens. Here we present results for a single quad image lensed by the \mockBC{} (upper) and \mockAC{} (lower) mock galaxies.
\textbf{Left:}
The ensemble average arrival time surface, with just the isocontours for the
saddle points drawn. The central diamonds show the reconstructed source
position across the entire ensemble.
\textbf{Middle:}
The surface density. The magenta curve represents the dark matter component,
the yellow curve the stellar component, and the blue curve is the sum of the two.
The black curve comes from the original mass model used to create the lens.
The vertical lines mark the radial positions of the images. The higher
resolution feature of \Glass\ has been used on the central pixel allowing the
steep profile to be captured.
\textbf{Right:}
The cumulative mass. The error bars on all plots are $1\sigma$, but the grey area shows the full range for DM+Stars (blue).}
\label{reconstruction}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.49\textwidth]{AAferror_profile-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BBferror_profile-1sig.pdf}\\
\includegraphics[width=0.49\textwidth]{ACferror_profile-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BCferror_profile-1sig.pdf}
\caption{Our main results showing the quality of model recovery \eqnrefp{ferror R} for all our test cases. 
Within
each panel are six groups of results for each of six lens morphologies. Each morphology
considered the presence of time delays (T,t) and a central image (M,m). The black markers are for tests
that did not include the stellar mass as a lower bound constraint, while the red markers
indicate where the stellar mass has been included. Error bars show the $1\sigma$ interval of the model ensemble.}
\label{main results}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.49\textwidth]{AAferror-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BBferror-1sig.pdf}\\
\includegraphics[width=0.49\textwidth]{ACferror-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BCferror-1sig.pdf}
\caption{Similar to \figref{main results}, we show here the fractional error
for the pixel-wise recovery \eqnrefp{ferror theta} of all models. The colors and labels are the same
as before. Error bars show the $1\sigma$ interval of the model ensemble.}
\label{main results pixel-wise}
\end{figure*}

@@

\begin{figure}
\plottwo{AAExtendedDoubleR1_TmS-shape-hist-11.pdf}{BCZContrastR1R3_TmS-shape-hist-212.pdf}
\caption{ \hilight{Larger labels.} The two plots in the left most column show sample distributions of
  $s=\lambda_1/\lambda_2$, the ratio of the largest to smallest principal axes.
  The upper (poor) plot is from the \mockAA{} galaxy, while the lower (good) plot is
  from the \mockBC{} galaxy. The black vertical lines mark the $2\sigma$
  region and the vertical blue line is the value of $s$ for the corresponding
mock galaxy. }
